The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2022-01-29 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd
4 minor comments from reviewer 1 are addressed

# Literature Review {#sec:litrev}
There is a voluminous literature on the effects of home-court advantage.
Many NBA home-court advantage studies analyze the effects by studying shooting
percentages. @Kotecki reported significant home-court advantage using performance-based
statistics, specifically field goal percentage, free throw percentage, and
points by comparing home performance vs. away performance in games.
All of which he showed significantly indicates that
home-court helps teams play better. @Cao studied the effects
of pressure on performance in the NBA. Using throws as their measure of
interest, they tested whether home
fans could distract and put pressure on opposing players to make free
throws. However, they found insignificant
evidence that home status has a substantial impact on missing from the free throw
line. @Harris used two point shots, three-point shots and free throws as measures
of interest to study home-court advantage. Two point shots were found to be
the strongest predictor of home-court advantage. They suggested
that home teams should try to shoot more two point shots and force
their opponent to take more two point shot attempts. This strategy will maximize
the benefits of home-court advantage and give them the best chance to win.

@@

There are also surveys on the factors contributing to home-court advantage.
@Carron1992 gave four main game location factors for home and away
teams, namely, the crowd factor, which is the impact of fans cheering; learning
factors, which is an advantage from home teams from playing at
a familiar venue; travel factors, the idea that away teams may face
fatigue and jet lag from traveling; and, rule factors, which says that home teams
may benefit from some advantages in rules and officiating. They acknowledge that
these factors would all be removed if games were played at a neutral site even
if one team was designated as “home team”. This study was reviewed a decade later
by @Carron2005. The 2005 review goes over the new findings from studies
about the significance of these four game location factors. Since 1992 they found
that results on these four factors are mixed. However, there is some evidence
supporting crowd and travel factors impact games in the NBA. There is less
evidence suggesting learning and rule factors impact the NBA. One interesting
finding cited by @Carron2005 is that in the absence of crowds result
in overall performance increases.

>>>>

# Literature Review {#sec:litrev}
There is a voluminous literature on the effects of home-court advantage.
Many NBA home-court advantage studies analyze the effects by studying shooting
percentages. @Kotecki reported significant home-court advantage using performance-based
statistics, specifically field goal percentage, free throw percentage, and
points by comparing home performance vs. away performance in games.
All of which he showed significantly indicates that
home-court helps teams play better. @Cao studied the effects
of pressure on performance in the NBA. Using free throws as their measure of
interest, they tested whether home
fans could distract and put pressure on opposing players to make free
throws. However, they did not find significant evidence
evidence that home status has a substantial impact on missing from the free throw
line. @Harris used two point shots, three-point shots and free throws as measures
of interest to study home-court advantage. Two point shots were found to be
the strongest predictor of home-court advantage. They suggested
that home teams should try to shoot more two point shots and force
their opponent to take more two point shot attempts. This minimum variance strategy will 
help home teams have a greater control of the game play and help maximize the benefits 
home court advantange.

@@

There are also surveys on the factors contributing to home-court advantage.
@Carron1992 gave four main game location factors for home and away
teams, namely, the crowd factor, which is the impact of fans cheering; learning
factors, which is an advantage from home teams from playing at
a familiar venue; travel factors, the idea that away teams may face
fatigue and jet lag from traveling; and, rule factors, which says that home teams
may benefit from some advantages in rules and officiating. They acknowledge that
these factors would all be removed if games were played at a neutral site even
if one team was designated as “home team”. This study was reviewed a decade later
by @Carron2005. The 2005 review goes over the new findings from studies
about the significance of these four game location factors. Since 1992 they found
that results on these four factors are mixed. However, there is some evidence
supporting crowd and travel factors impact games across all major sports. There is less
evidence suggesting learning and rule factors impact across the various collegiate 
and professional sports, regardless, the NBA is not a league which has rules that
may favor the home team like batting last in the MLB. One interesting finding cited by @Carron2005 is that in the absence of crowds result in overall performance increases.
